Exploring probability distributions for bivariate temporal granularities

### 2019-09-13 main.Rmd
trying out graphics relevant for analysis

#over_inning    ball_over 
cricket_tsibble %>% granplot("over_inning", "ball_over",
  hierarchy_model,
  response = "total_runs",
  plot_type = "violin"

@@

cricket_tsibble %>% granplot("inning_match", "ball_over",
  hierarchy_model,
  response = "total_runs"
)

# inning_match   ball_inning

cricket_tsibble %>% granplot("inning_match", "ball_inning",
  hierarchy_model,
  response = "total_runs"
)

@@

cricket_tsibble %>% granplot("ball_over", "over_inning",
  hierarchy_model,
  response = "total_runs"
)

@@

>>>>

#over_inning    ball_over 
cricket_tsibble %>% granplot("over_inning", "ball_over",
  hierarchy_model,
  response = "total_runs",
  plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)

@@

cricket_tsibble %>% granplot("inning_match", "ball_over",
  hierarchy_model,
  response = "total_runs",
   plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)
)

# inning_match   ball_inning 
#interesting plot
cricket_tsibble %>% granplot("inning_match", "ball_inning",
  hierarchy_model,
  response = "total_runs",
   plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))+
  scale_x_discrete(breaks = seq(1,120,5))

@@

cricket_tsibble %>% granplot("ball_over", "over_inning",
  hierarchy_model,
  response = "total_runs",
  plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))
)

@@

cricket_tsibble %>% granplot("ball_over", "over_match",
  hierarchy_model,
  response = "total_runs"
) + scale_color_brewer(type = "div", palette = "Dark2")
